Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-10-29 paper.tex
Edits according to suggestions from Mark

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed by the high-redshift galaxy
community.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

@@

We know little about dust distributions in low-redshift dusty galaxies, which
have high IR luminosities and low-to-high emergent UV luminosities.  Their
IR emitting regions span a range of sizes, from sub- to several kpc
\citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
even harder.  If a dusty galaxy's measured H$\alpha$ escape fraction agreed with
the prediction from the \citet{calzetti00} attenuation formula, we might
conclude that the galaxy has a uniform dust distribution only if we believe
that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
escape fraction disagreed with the prediction from the \citet{calzetti00}
formula, the galaxy might have a nonuniform dust distribution, like that of a
dust-poor galaxy.  This explanation for the disagreement is not unique.  The
galaxy might have a uniform distribution and obey a different $k(\lambda)$.

@@

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
image and generally has low values of UV and H$\alpha$ escape fractions.  The
samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

The final quantity of interest for each matched source is an H$\alpha$ line
flux or flux limit.  These come from our reduction of observations from the
\emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
We match each 100$\,\micron$ source to a counterpart in the direct image
accompanying the grism observations.  Two people in our group visually inspect
the counterpart's spectrum and then review and reconcile any discrepant redshift
assignments.  The
H$\alpha$ line falls in the grism's wavelength range for galaxies at
$0.7 < z < 1.5$.  The spectra have low enough wavelength resolution that the
H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
at $\lambda = 0.6583\,\micron$ is 0.3 times the H$\alpha$ line flux and that
the line flux of [N II] at $\lambda = 0.6548\,\micron$ is 0.1 times the
H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
gas-phase metallicity so these values may be incorrect for some star-forming
galaxies.
The values will be correct for a significant fraction of galaxies in our
sample if the sample has a distribution of
gas-phase metallicity similar to that of low-redshift galaxies
\citep{kauffmann03}.  The values will be correct for a larger fraction of
galaxies in our sample if the sample has a distribution of gas-phase
metallicity similar to that of low-redshift galaxies which are luminous in
the near-IR \citep{weiner07}.  For each 1D spectrum with a visible and
uncontaminated
line complex, we fit a linear model to the continuum and Gaussian profiles to
the emission lines and extract the H$\alpha$ line flux.  The uncertainty on the
line flux comes from the covariance matrix times the fit's reduced $\chi^{2}$.
We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
fluxes and limits by 1.1 as an aperture correction.

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of: \citet{lefevre04,szokoly04,mignoli05,yamada05,ravikumar07,
vanzella08,lilly09,balestra10,fadda10,simpson12,kurk13,santini14}; Simpson et
al. (in prep.); Almaini et al. (in prep.); and
M. Dickinson (private communication).  Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
The direct
image is the image taken as part of the grism observations.  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

@@

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  If the galaxy has one
measured IR flux density, we find the SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

@@

We estimate an emergent UV luminosity or a
limit at rest-frame 0.16$\,\micron$ for each galaxy using its redshift and
the power-law fit to the rest-frame UV flux densities.  We refer to the
luminosity as $0.16 \times L_{0.16}$.

@@

Three star formation rates allow us to compare two attenuation values.
We eschew magnitude attenuation in favor of the escape fraction, which
is the ratio of emergent to intrinsic luminosity.  We define the following
quantities.
\begin{itemize}
\item \alephuv~is the escape fraction at rest-frame 0.16$\,\micron$.  In
relation to A$_{\mathrm{UV}}$,
f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
\item \alephha~is the escape fraction of the H$\alpha$ line luminosity.
\item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
wavelength of H$\alpha$---the attenuation formula prediction.  For the
attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
\end{itemize}

@@

The H$\alpha$ escape fractions in \citet{calzetti94} come from the ratios of
H$\alpha$ to H$\beta$
line luminosities.  In the absence of dust the ratio is 2.86, so
($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86~=~\alephha/\alephhb.  Since
\alephhb~is a power-law function of \alephha, the ratio of line luminosities
uniquely determines \alephha.

The UV and 0.66$\,\micron$ escape fractions in \citet{calzetti94} come from
comparing spectra of
galaxies with H$\alpha$ escape fractions of 1 to spectra of galaxies with
H$\alpha$ escape fractions less than 1.  The H$\alpha$ and H$\beta$ lines in
the spectra must be masked or replaced with continuum values.  The literature
relation is technically
\alephha~= \alephuvha$^{2.3}$.  \citet{calzetti97b} uses the Milky Way
extinction formula of \citet{howarth83} to determine H$\alpha$ escape
fractions for low-redshift dust-poor galaxies; if we instead use the
attenuation formula, we get \alephha~= \alephuvha$^{2.1}$.

@@

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation (rederived in the same paper).  This
relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

@@

The escape fraction relations of dusty galaxies are subject to selection
effects.  The best-fit relation for the low-redshift dusty galaxies seems to:
(1) underestimate H$\alpha$ escape fractions at low UV escape fractions; and (2)
overestimate H$\alpha$ escape fractions at high UV escape fractions (top
right panel of Fig. \ref{fha_fuv}).  This may reflect our constraint that
\alephha~=1 when
\alephuv~=1, but the lack of galaxies with H$\alpha$ escape fractions at or
below the relation may be due to galaxies with H$\alpha$ SFRs below the limit
of the sample.  We do not measure H$\alpha$ line flux limits for galaxies that
meet the selection criteria of \citet{hwang13} and have undetected H$\alpha$
line fluxes.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to the minimum H$\alpha$ line flux of the sample, we fill in the space around
the relation.

High-redshift dusty galaxies with UV escape fractions $< 10^{-2}$ seem to have
less dispersion in their H$\alpha$ escape fractions than do galaxies with UV
escape fractions $> 10^{-2}$.  Despite our best efforts to measure H$\alpha$
line flux limits, we still lack them for galaxies lacking spectroscopic
redshifts.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to a reasonable H$\alpha$ line flux limit for the grism observations
($5 \times 10^{-17}$ erg s$^{-1}$ cm$^{-2}$), we fill in the space with low
H$\alpha$ escape fractions at low UV escape fractions.  The decrease in
dispersion is probably an artifact of the grism detection limit and a paucity
of spectroscopic redshifts in UDS and the part of COSMOS in CANDELS.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.365]{fha_fuv.eps}
\caption{{\small \emph{Top left}: The H$\alpha$ escape fraction, \alephha, as a
function of the UV
escape fraction, \alephuv, for the low-redshift
dust-poor galaxies.  The dashed purple line shows \alephuvha, the extrapolation
of \alephuv~to the wavelength of H$\alpha$ using the \citet{calzetti00}
attenuation formula, as a function of \alephuv.  This is the uniform dust
distribution hypothesis for this attenuation formula.  \citet{calzetti97b}, who
study another sample of low-redshift dust-poor galaxies, find
that H$\alpha$ escape fractions are lower than this extrapolation (dotted black
line).  We find a similar result (solid orange line).
We have some confidence that our H$\alpha$ escape fractions are grossly
correct.
\emph{Top right}:  \alephha~as a function of \alephuv~for the low-redshift dusty
galaxies.  In
low-redshift dusty galaxies, regions with ionizing stars have lower
escape fractions than the extrapolation and higher escape fractions than they
would have in low-redshift dust-poor galaxies.
\emph{Bottom left}:  \alephha~as a function of \alephuv~for the high-redshift
dusty galaxies.  In high-redshift dusty galaxies,
regions with ionizing stars have
lower escape fractions than the extrapolation and higher escape fractions than
they would have in low-redshift dust-poor galaxies.  A conclusion about the
uniformity of dust distributions in high-redshift dusty galaxies is subject to
an assumption about the attenuation formula.\label{fha_fuv}}}
\end{figure}

@@

\bibitem[Santini et al.(2014)]{santini14} Santini, P., Ferguson, 
H.~C., Fontana, A., et al.\ 2014, arXiv:1412.5180

>>>>

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed by the high-redshift galaxy
community.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the Calzetti attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

@@

We know little about dust distributions in low-redshift dusty galaxies, which
have high IR luminosities and wide-ranging emergent UV luminosities.  Their
IR emitting regions span a range of sizes, from sub- to several kpc
\citep{diaz10}.  Measuring a size is hard enough; imaging a distribution is
even harder.  If a dusty galaxy's measured H$\alpha$ escape fraction agreed with
the prediction from the \citet{calzetti00} attenuation formula, we might
conclude that the galaxy has a uniform dust distribution only if we believe
that the prediction is valid.  If a dusty galaxy's measured H$\alpha$
escape fraction disagreed with the prediction from the \citet{calzetti00}
formula, the galaxy might have a nonuniform dust distribution, like that of a
dust-poor galaxy.  This explanation for the disagreement is not unique.  The
galaxy might have a uniform distribution and obey a different $k(\lambda)$.

@@

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
generally has high values of UV and
H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from a
mid- or far-IR
image and generally has low values of UV and H$\alpha$ escape fractions.  The
samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

The final quantity of interest for each matched source is an H$\alpha$ line
flux or flux limit.  These come from our reduction of observations from the
\emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
We match each 100$\,\micron$ source to a counterpart in the direct image
accompanying the grism observations.  Two people in our group visually inspect
the counterpart's spectrum and then review and reconcile any discrepant redshift
assignments.  The
H$\alpha$ line falls in the grism's wavelength range for galaxies at
$0.7 < z < 1.5$.  The spectra have low enough wavelength resolution that the
H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
at $\lambda = 0.6583\,\micron$ is 0.3 times the H$\alpha$ line flux and that
the line flux of [N II] at $\lambda = 0.6548\,\micron$ is 0.1 times the
H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
gas-phase metallicity so these values may be incorrect for some star-forming
galaxies.
The values will be correct for a significant fraction of galaxies in our
sample if the sample has a distribution of
gas-phase metallicity similar to that of low-redshift galaxies
\citep{kauffmann03}.  The values will be correct for a larger fraction of
galaxies in our sample if the sample has a distribution of gas-phase
metallicity similar to that of low-redshift galaxies which are luminous in
the near-IR \citep{weiner07}.  For each 1D spectrum with a visible and
uncontaminated
line complex, we fit a linear model to the continuum and Gaussian profiles to
the emission lines and extract the H$\alpha$ line flux.  The uncertainty on the
line flux comes from the covariance matrix times the fit's reduced $\chi^{2}$.
We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
fluxes and limits by 1.1, the aperture correction.

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of:
\citet{lefevre04,szokoly04,mignoli05,ravikumar07,vanzella08,
balestra10,fadda10,kurk13,santini14}; and M. Dickinson (private communication)
for GOODS-S;
\citet{yamada05,simpson12}; Simpson et al. (in prep.); and
Almaini et al. (in prep.) for UDS; and \citet{lilly09} for COSMOS.  Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
The direct
image is the image taken as part of the grism observations.  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

@@

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities ($S_{\nu}$
units) at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  Each template SED has
an IR luminosity.  If the galaxy has one
measured flux density at a rest-frame wavelength between 8 and 1000$\,\micron$,
we find the redshifted SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

@@

We estimate an emergent UV luminosity or a
limit at rest-frame 0.16$\,\micron$ for each galaxy using its redshift and
the power-law fit to the rest-frame UV flux densities.  We refer to the
luminosity as $0.16 \times L_{0.16}$.  Fig. \ref{lir_luv} shows the IR and UV
luminosities for all galaxies in our samples.  We emphasize that we use
the adjective ``dusty'' because the average galaxy in the sample has a lower
UV luminosity and a higher IR luminosity than does the average galaxy in the
``dust-poor'' sample.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.44]{lir_luv_sample.eps}
\caption{IR luminosity vs. emergent UV luminosity for the samples of dusty
and dust-poor galaxies.\label{lir_luv}}
\end{figure}

@@

Three star formation rates allow us to compare two attenuation values.
We eschew magnitude attenuation in favor of the escape fraction, which
is the ratio of emergent to intrinsic luminosity.  We define the following
quantities.
\begin{itemize}
\item \alephuv~is the escape fraction of the continuum
at rest-frame 0.16$\,\micron$.  In
relation to A$_{\mathrm{UV}}$,
f$_{\mathrm{esc}}$(0.16$\,\micron$) = 10$^{-\mathrm{A}_{\mathrm{UV}}/2.5}$.
\item \alephha~is the escape fraction of the H$\alpha$ emission line luminosity.
\item \alephuvha~is the escape fraction extrapolated from \alephuv~to the
wavelength of H$\alpha$---the attenuation formula prediction for the escape
fraction at rest-frame 0.66$\,\micron$.  For the
attenuation formula in \citet{calzetti00}, \alephuvha~= \alephuv$^{0.33}$.
\end{itemize}

@@

The H$\alpha$ escape fractions in \citet{calzetti94} come from the ratios of
H$\alpha$ to H$\beta$
line luminosities.  In the absence of dust and for Case B recombination
the ratio is 2.86, so
($L_{\mathrm{H}\alpha}$/$L_{\mathrm{H}\beta}$)/2.86 = \alephha/\alephhb.  Since
they assume that \alephhb~is a power-law function of \alephha, the ratio of line
luminosities uniquely determines \alephha.

The UV and 0.66$\,\micron$ escape fractions in \citet{calzetti94} come from
comparing spectra of
galaxies with H$\alpha$ escape fractions of 1 to spectra of galaxies with
H$\alpha$ escape fractions less than 1.  The H$\alpha$ and H$\beta$ lines in
the spectra must be masked or replaced with continuum values.  The literature
relation is technically
\alephha~= \alephuvha$^{2.3}$.  \citet{calzetti97b} uses the Milky Way
extinction formula of \citet{howarth83} to determine H$\alpha$ escape
fractions for low-redshift dust-poor galaxies; if we instead use the
Calzetti attenuation formula, we get \alephha~= \alephuvha$^{2.1}$.

@@

The sample, from \citet{overzier11}, contains galaxies that lie roughly on
the low-redshift IRX-$\beta$ relation (rederived in the same paper).  IRX
is IR luminosity divided by emergent UV luminosity.  This
relation is a blunt instrument we
use to determine whether or not galaxies obey an attenuation formula at UV
wavelengths; \alephuv~is a function of IRX and an attenuation formula relates
\alephuv~to $\beta$.  Since these galaxies lie on the relation, we
expect them to have dust properties that conform with the properties of
the galaxies in the \citet{calzetti00} sample.  We calculate \alephha~and
\alephuv~for each galaxy in the following way.
\begin{itemize}
\item \alephuv~= ($L_{\mathrm{IR}}$/($1.68\times0.16\times
L_{\mathrm{0.16}}$)+1)$^{-1}$.  This is equivalent to \alephuv~= (emergent UV
SFR)/(IR SFR + emergent UV SFR).
%\item \alephuvha~= \alephuv$^{0.33}$.
\item Following the assumptions in \ref{sfrs}: \alephha~=
(emergent H$\alpha$ SFR)/(IR SFR + emergent UV SFR).
\end{itemize}
We use these quantities to find, for the sample, a best-fit power-law index $q$
for the form \alephha~= \alephuv$^{q}$.

@@

The escape fraction relations of dusty galaxies are subject to selection
effects.  The best-fit relation for the low-redshift dusty galaxies seems to:
(1) underestimate H$\alpha$ escape fractions at low UV escape fractions; and (2)
overestimate H$\alpha$ escape fractions at high UV escape fractions (top
right panel of Fig. \ref{fha_fuv}).  This may reflect our constraint that
\alephha~= 1 when
\alephuv~= 1, but the lack of galaxies with H$\alpha$ escape fractions at or
below the best-fit relation may be due to galaxies with H$\alpha$ SFRs below the limit
of the sample.  We do not measure H$\alpha$ line flux limits for galaxies that
meet the selection criteria of \citet{hwang13} and have undetected H$\alpha$
line fluxes.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to the minimum H$\alpha$ line flux of the sample, we fill in the space around
the relation.

High-redshift dusty galaxies with UV escape fractions $< 10^{-2}$ seem to have
less dispersion in their H$\alpha$ escape fractions than do galaxies with UV
escape fractions $> 10^{-2}$.  Despite our best efforts to measure H$\alpha$
line flux limits, we still lack them for galaxies lacking spectroscopic
redshifts.  If we replace all H$\alpha$-detected SFRs with SFRs corresponding
to a reasonable H$\alpha$ line flux limit for the grism observations
\citep[$5 \times 10^{-17}$ erg s$^{-1}$ cm$^{-2}$,][]{brammer12}, we fill in the space with low
H$\alpha$ escape fractions at low UV escape fractions.  The decrease in
dispersion is probably an artifact of the grism detection limit and a paucity
of spectroscopic redshifts in UDS and the part of COSMOS in CANDELS.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.365]{fha_fuv.eps}
\caption{{\small \emph{Top left}: The H$\alpha$ escape fraction, \alephha, as a
function of the UV
escape fraction, \alephuv, for the low-redshift
dust-poor galaxies.  The dashed purple line shows \alephuvha, the extrapolation
of \alephuv~to the wavelength of H$\alpha$ using the \citet{calzetti00}
attenuation formula, as a function of \alephuv.  This is the uniform dust
distribution hypothesis for this attenuation formula.  \citet{calzetti97b}, who
study another sample of low-redshift dust-poor galaxies, find
that H$\alpha$ escape fractions are lower than this extrapolation (dotted black
line).  We find a similar result (solid orange line).
We have some confidence that our H$\alpha$ escape fractions are grossly
correct.
\emph{Top right}:  \alephha~as a function of \alephuv~for the low-redshift dusty
galaxies.  In
low-redshift dusty galaxies, regions with ionizing stars have lower
escape fractions than the extrapolation and higher escape fractions than they
would have in low-redshift dust-poor galaxies.
\emph{Bottom left}:  \alephha~as a function of \alephuv~for the high-redshift
dusty galaxies.  In high-redshift dusty galaxies,
regions with ionizing stars have
lower escape fractions than the extrapolation and higher escape fractions than
they would have in low-redshift dust-poor galaxies.\label{fha_fuv}}}
\end{figure}

@@

\bibitem[Santini et al.(2015)]{santini14} Santini, P., Ferguson, 
H.~C., Fontana, A., et al.\ 2015, \apj, 801, 97
